---
title: Inspecting linkage reliability across bio data
output: html_notebook
---

```{r, include=FALSE}
if (interactive()) {
  targets::tar_config_set(store = here::here("_targets"))
}
```


I'm using eSense file count as a proxy for total sessions as there is currently one file per participant per wave. Matching Mirage to eSense is the first step of finding the correct window.

In theory, eSense and Mirage were collected on the same tablet, so the clock times should be compatible to at least the second.

```{r}
targets::tar_load(esense_meta)
targets::tar_load(mirage_windows)

# Using DuckDB
conn <- duckdb::dbConnect(duckdb::duckdb(), ":memory:")
duckdb::duckdb_register(conn, "esense", esense_meta)
duckdb::duckdb_register(conn, "mirage", mirage_windows)
```

Mirage comes in a stream of events. I have selected on the "play" and "baseline" events for now. They are processed using a stack to capture any nested events.

```{sql, connection = conn}
SELECT * FROM mirage USING SAMPLE 100;
```

```{sql, connection = conn}
WITH cte AS (
  SELECT DISTINCT mirage_pid
    , device
    , length_secs
    , start_time
    , end_time
  FROM esense 
  WHERE tz = 'bd'
)
SELECT * FROM cte USING SAMPLE 100;
```

From some manual inspection, it appears that eSense and Mirage window ends are around the same time, so this creates an ability to pick which is the correct time zone
for the eSense data. I am taking the absolute value of the difference, but in most cases eSense ends afterwards.

```{sql, connection = conn}
CREATE TABLE me_merge AS WITH e AS (
  SELECT *
    , date_trunc('day', start_time) AS date
  FROM esense
), m AS (
  SELECT *
    , date_trunc('day', start) AS date
  FROM mirage
), cte AS (
  SELECT e.mirage_pid AS mirage_pid
    , e.date AS date
    , m.start AS start_m
    , e.start_time AS start_e
    , m.end AS end_m
    , e.end_time AS end_e
    , e.tz AS tz
    , e.path AS file_esense
    , m.id AS row_mirage
  FROM m
  LEFT JOIN e ON
    m.mirage_pid = e.mirage_pid AND
    m.date = e.date
), cte1 AS (
  SELECT *
    , @date_diff('minutes', end_e, end_m) AS diff_end
  FROM cte
)
SELECT *
  , min(diff_end) OVER (PARTITION BY mirage_pid, date ORDER BY diff_end) AS min_diff_end
FROM cte1
QUALIFY diff_end = min_diff_end;
```

```{sql, connection = conn}
FROM me_merge LIMIT 100;
```

It looks like there are many ties with the Bangladesh and Almaty "timezone" entries. Since we've already calculated the time lag
and considered the differences, if we exclude the `tz` column and take a `DISTINCT` these ties should be resolved.

```{sql, connection = conn}
CREATE TABLE me_merge_distinct AS SELECT DISTINCT * EXCLUDE (tz) FROM me_merge;
```

As of May 2024, we only have Mirage up to a certain point, so recovery calculations must account for this.

```{sql, connection = conn}
WITH cte AS (
  SELECT e.path AS path
    , CASE WHEN m.row_mirage IS NULL THEN 0 ELSE 1 END AS record_match
    , date_trunc('day', e.start_time) AS date_esense
    , m.date AS date_merged
  FROM esense e
  LEFT JOIN me_merge_distinct m ON e.path = m.file_esense
)
SELECT 100 * sum(record_match) / COUNT(*) AS pct_recovery 
FROM cte
WHERE date_esense <= (SELECT max(date_merged) FROM cte)
```

This is a reasonable automated recovery rate, enough to go forward with this approach for the editors.
Finding the eSense files that don't match might be a task for another time and may not be worth it.

The final step is to synchronize Bodyguard. 
Since we have the eSense to Mirage linkage, we can scan for other Mirage events that happen within the same 1 or 2 hours (later inspection will validate) of the Mirage event that matches eSense. 
These Mirage events then can put us in the right temporal zone to filter the Bodyguard files.

```{r, include=FALSE}
DBI::dbDisconnect(conn)
```





