---
title: Inspecting linkage reliability across bio data
output: html_notebook
---

```{r, include=FALSE}
if (interactive()) {
  targets::tar_config_set(store = here::here("_targets"))
  source(here::here("projects/prelude.R"))
}
```


I'm using eSense file count as a proxy for total sessions as there is currently one file per participant per wave. Matching Mirage to eSense is the first step of finding the correct window.

In theory, eSense and Mirage were collected on the same tablet, so the clock times should be compatible to at least the second.

```{r}
targets::tar_load(esense_meta)
targets::tar_load(mirage_windows)
targets::tar_load(bg_files)
targets::tar_load(linked_ecg_recordings)

# Using DuckDB
conn <- duckdb::dbConnect(duckdb::duckdb(), ":memory:")
duckdb::duckdb_register(conn, "esense", esense_meta)
duckdb::duckdb_register(conn, "mirage", mirage_windows)

linked_recordings <- linked_ecg_recordings |>
  tidytable::bind_rows()

duckdb::duckdb_register(conn, "linked_bg_mirage", linked_recordings)
```

Mirage comes in a stream of events. I have selected on the "play" and "baseline" events for now. They are processed using a stack to capture any nested events.

```{sql, connection = conn}
SELECT * FROM mirage USING SAMPLE 100;
```

```{sql, connection = conn}
WITH cte AS (
  SELECT DISTINCT mirage_pid
    , device
    , length_secs
    , start_time
    , end_time
  FROM esense 
  WHERE tz = 'bd'
)
SELECT * FROM cte USING SAMPLE 100;
```

From some manual inspection, it appears that eSense and Mirage window ends are around the same time, so this creates an ability to pick which is the correct time zone
for the eSense data. I am taking the absolute value of the difference, but in most cases eSense ends afterwards.

```{sql, connection = conn}
CREATE TABLE me_merge AS WITH e AS (
  SELECT *
    , date_trunc('day', start_time) AS date
  FROM esense
), m AS (
  SELECT *
    , date_trunc('day', start) AS date
  FROM mirage
), cte AS (
  SELECT e.mirage_pid AS mirage_pid
    , e.date AS date
    , m.start AS start_m
    , e.start_time AS start_e
    , m.end AS end_m
    , e.end_time AS end_e
    , e.tz AS tz
    , e.path AS file_esense
    , m.id AS row_mirage
  FROM m
  LEFT JOIN e ON
    m.mirage_pid = e.mirage_pid AND
    m.date = e.date
), cte1 AS (
  SELECT *
    , @date_diff('minutes', end_e, end_m) AS diff_end
  FROM cte
)
SELECT *
  , min(diff_end) OVER (PARTITION BY mirage_pid, date ORDER BY diff_end) AS min_diff_end
FROM cte1
QUALIFY diff_end = min_diff_end;
```

```{sql, connection = conn}
FROM me_merge LIMIT 100;
```

It looks like there are many ties with the Bangladesh and Almaty "timezone" entries. Since we've already calculated the time lag
and considered the differences, if we exclude the `tz` column and take a `DISTINCT` these ties should be resolved.

```{sql, connection = conn}
CREATE TABLE me_merge_distinct AS SELECT DISTINCT * EXCLUDE (tz) FROM me_merge;
```

As of May 2024, we only have Mirage up to a certain point, so recovery calculations must account for this.

```{sql, connection = conn}
WITH cte AS (
  SELECT e.path AS path
    , CASE WHEN m.row_mirage IS NULL THEN 0 ELSE 1 END AS record_match
    , date_trunc('day', e.start_time) AS date_esense
    , m.date AS date_merged
  FROM esense e
  LEFT JOIN me_merge_distinct m ON e.path = m.file_esense
)
SELECT 100 * sum(record_match) / COUNT(*) AS pct_recovery 
FROM cte
WHERE date_esense <= (SELECT max(date_merged) FROM cte)
```

This is a reasonable automated recovery rate, enough to go forward with this approach for the editors.
Finding the eSense files that don't match might be a task for another time and may not be worth it.

The final step is to synchronize Bodyguard. 
Since we have the eSense to Mirage linkage, we can scan for other Mirage events that happen within the same 1 or 2 hours (later inspection will validate) of the Mirage event that matches eSense. 
These Mirage events then can put us in the right temporal zone to filter the Bodyguard files.

```{sql, connection = conn}
CREATE TABLE m AS SELECT *
  , date_trunc('day', start) AS date
FROM mirage;
```

```{sql, connection = conn}
CREATE OR REPLACE TEMP SEQUENCE idx START 1;
```

```{sql, connection = conn}
CREATE TABLE mirage_sessions AS
WITH raw_pairs AS (
  SELECT a.id AS id_a
  , b.id AS id_b
  FROM (SELECT id FROM m) a
  , (SELECT id FROM m) b
), adorned_pairs AS (
  SELECT id_a, id_b
  , a.start AS start_a
  , a.date AS date_a
  , a.mirage_pid AS mpid_a
  , b.start AS start_b
  , b.date AS date_b
  , b.mirage_pid AS mpid_b
  FROM raw_pairs
  LEFT JOIN (SELECT id, "start", date, mirage_pid FROM m) a
    ON a.id = raw_pairs.id_a
  LEFT JOIN (SELECT id, "start", date, mirage_pid FROM m) b
    ON b.id = raw_pairs.id_b
), raw_diffs AS (
  SELECT mpid_a AS mirage_pid
    , date_a AS date
    , id_a
    , id_b
    , start_a
    , start_b
    , date_diff('ms', start_a, start_b) / 1000 AS dt
  FROM adorned_pairs
  WHERE date_a = date_b AND mpid_a = mpid_b
), cleaned_diffs AS (
  SELECT * REPLACE (
    CASE WHEN id_a = id_b AND start_a = start_b THEN NULL ELSE dt END AS dt
  ) 
  FROM raw_diffs
), cte AS (
  SELECT *
    , mad(dt) OVER (
      PARTITION BY mirage_pid, date, id_a
    ) AS mad_dt
  FROM cleaned_diffs c
  LEFT JOIN (
    SELECT mirage_pid, date, nextval('idx') AS id_session
    FROM cleaned_diffs
    GROUP BY 1, 2
  ) s
    USING (mirage_pid, date)
  ORDER BY mirage_pid, date, id_a
), cte2 AS (
  SELECT *
  FROM (
    SELECT mirage_pid
      , date
      , COLUMNS('^id_')
      , COLUMNS('^start_')
      , dt
      , mad_dt
      , min(mad_dt) OVER (PARTITION BY id_session) AS min_mad_dt
    FROM cte
  ) 
  WHERE mad_dt = min_mad_dt OR min_mad_dt IS NULL
), cte3 AS (
  SELECT *
    , min(id_a) OVER (PARTITION BY id_session) AS id_event_root
  FROM cte2
)
SELECT id_session
  , mirage_pid
  , date
  , id_b AS id_event
  , ifnull(abs(dt) < (60 * 60), true) AS valid_event -- NULL would mean single event session
FROM cte3
WHERE id_a = id_event_root
```

```{sql, connection = conn}
SELECT * FROM mirage_sessions LIMIT 1000;
```

This finds all neighboring Mirage events to the "parent" eSense linked event (parent could also mean mother, but I mean parent/child in a graph relationship).
With these events linked, now the Bodyguard files can be linked to the parent **and** child Mirage events.

```{sql, connection = conn}
CREATE TABLE linked_mirage_sessions AS
SELECT *
  , id_session IN (
    SELECT id_session 
    FROM mirage_sessions
    WHERE valid_event AND id_event IN (
      SELECT row_mirage FROM me_merge_distinct
    )
  ) AS linked_esense
  , id_session IN (
    SELECT id_session
    FROM mirage_sessions
    WHERE id_event IN (
      SELECT id_mirage FROM linked_bg_mirage
    )
  ) AS linked_bg
FROM mirage_sessions
```

From this comparison, we can compute the Mirage<->eSense and Mirage<->Bodyguard record linkages;

```{r}
res <- data.table::as.data.table(
  DBI::dbGetQuery(conn, "SELECT DISTINCT id_session, linked_esense, linked_bg FROM linked_mirage_sessions;")
)

res[, table(linked_esense, linked_bg) / .N]
```

```{r, include=FALSE}
DBI::dbDisconnect(conn)
```
